Supplementary Materials

### 2020-10-14 Writeup/manuscript.tex
minor edits

The current data provide a complete description of the visual system’s response to symmetries in the 2-D plane. Our design precludes us from independently measure the response to P1, but because each of the 16 other groups produce non-zero odd harmonic amplitudes (see Figure 1), we can conclude that the relationships between P1 and all other groups, where P1 is the subgroup, are also preserved by the visual system. The subgroup relationships are in many cases not obvious perceptually, and most participants had no knowledge of group theory. Thus, the visual system’s ability to preserve the subgroup hierarchy does not depend on explicit knowledge of the relationships. Furthermore, previous behavioral experiments have shown that although naïve observers can distinguish many of the wallpaper groups \cite{RN1253}, they are generally error-prone when asked to assign exemplar images to the appropriate group \cite{RN172} \textcolor{red}{ALASDAIR PERHAPS YOU WANT TO SAY MORE OR DIFFERENT HERE}.

>>>>

The current data provide a complete description of the visual system’s response to symmetries in the 2-D plane. Our design precludes us from independently measure the response to P1, but because each of the 16 other groups produce non-zero odd harmonic amplitudes (see Figure 1), we can conclude that the relationships between P1 and all other groups, where P1 is the subgroup, are also preserved by the visual system. The subgroup relationships are in many cases not obvious perceptually, and most participants had no knowledge of group theory. Thus, the visual system’s ability to preserve the subgroup hierarchy does not depend on explicit knowledge of the relationships. Furthermore, previous behavioral experiments have shown that although naïve observers can distinguish many of the wallpaper groups \cite{RN1253}, \textcolor{green}{when asked to sort exampler images into visually similar subsets, they tend to make between four and 12 sets. It is common for examplars from two distinct symmetry groups to be judged as belonging to the same subset, and also for examplars from the same group to be placed into disjoint similarity subsets.}

### 2020-10-14 analysis/analysis.Rmd
minor edits

```{r}
d_dispthresh %>% 
  group_by(subject) %>% 
  summarise(count = n()) %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

@@

comparison_summary <- function(subgroup_comp_dat, greater, measurement_lab) {
  # compute probabilties
  subgroup_comp_dat %>%
    group_by(key, index, normal) %>%
    summarise(
      mean_value = mean(value),
      prob_one_tailed = if_else(greater == TRUE, mean(value > 0), mean(value < 0)))  %>%
    mutate(
      prob_one_tailed = if_else(prob_one_tailed==0, 0.01, prob_one_tailed),
      measurement = measurement_lab,
      index_labs = as.numeric(as.factor(index)),
      lab_cols = v_cols[index_labs],
      prob_cat = cut(prob_one_tailed, c(0, 0.5, 0.75, 0.9, 0.99, 1))) -> comp_summary_dat

@@

It is unclear from the above summary tables whether either variable has a clear effect. We can use leave-one-out metrics to compare models.

```{r}
summary(lm(data = comp_summary$threshold, mean_value ~ index * normal))
summary(lm(data = comp_summary$eeg, mean_value ~ index * normal))

>>>>

```{r}
d_dispthresh %>% 
  group_by(subject) %>% 
  summarise(count = n(), .groups = "drop") %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

@@

comparison_summary <- function(subgroup_comp_dat, greater, measurement_lab) {
  # compute probabilties
  subgroup_comp_dat %>%
    group_by(key, index, normal) %>%
    summarise(
      mean_value = mean(value),
      prob_one_tailed = if_else(greater == TRUE, mean(value > 0), mean(value < 0)),
      .groups = "drop")  %>%
    mutate(
      prob_one_tailed = if_else(prob_one_tailed==0, 0.01, prob_one_tailed),
      measurement = measurement_lab,
      index_labs = as.numeric(as.factor(index)),
      lab_cols = v_cols[index_labs],
      prob_cat = cut(prob_one_tailed, c(0, 0.5, 0.75, 0.9, 0.99, 1))) -> comp_summary_dat

@@

It is unclear from the above summary tables whether either variable has a clear effect.
